### 2024-06-04 acronyms/acronyms.tex
ies

\newacronym{nrs}{NRHES}{Nuclear Renewable Hybrid Energy System}

@@

@@

@@

%Add \input{$ACRONYM/acronyms} in the preamble, where $ACRONYM is the /path/to/file

>>>>

vnewacronym{nrs}{NRHES}{Nuclear Renewable Hybrid Energy System}

@@

\newacronym{ferc}{FERC}{Federal Energy Regulatory Commission}

@@

\newacronym{kwh}{kWh}{Kilowatt-Hour}
\newacronym{ocm}{OCRWM}{Office of Civilian Radioactive Waste Management}
\newacronym{dot}{DOT}{Department of Transportation}
\newacronym{mrs}{MRS}{Monitored Retrievable Storage}
\newacronym{nju}{NJUS}{Nome Joint Utility System}
\newacronym{irr}{IRR}{Internal Rate of Return}
\newacronym{tci}{TCI}{Total Capital Investment}
\newacronym{lce}{LCOE}{Levelized Cost of Electricity}
\newacronym{npv}{NPV}{Net Present Value}
\newacronym{lcs}{LCOS}{Levelized Cost of Storage}
\newacronym{lac}{LACE}{Levelized Avoided Cost of Electricity}
\newacronym{ece}{ECOE}{Effective Cost of Energy}
\newacronym{llp}{LOLP}{Loss of Load Probability}
\newacronym{ies}{IES}{Integrated Energy System}
\newacronym{nrl}{NREL}{National Renewable Energy Laboratory}
\newacronym{hop}{HOPP}{Hybrid Optimization and Performance Platform}
\newacronym{lch}{LCOH}{Levelized Cost of Hydrogen}
\newacronym{fom}{FOM}{Figure of Merit}

@@

%Add \input{$ACRONYM/acronyms} in the preamble, where $ACRONYM is the /path/to/file/
